---
title: "pH Cleaning"
author: "Anson Ekau"
date: "2023-07-14"
output: html_document
---

#Load in packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```


# Read in Dissolved Oxygen data — 4 sets

```{r OctNov2022 Kalauhaihai, message=FALSE, warning=FALSE}
data_pH_OctNov2022_Kalauhaihai <- read_tsv(here("raw_data/raw_pH/data_pH_OctNov2022_Kalauhaihai_20839036.txt"))
```

```{r FebApr2023 Kalauhaihai, message=FALSE, warning=FALSE}
data_pH_FebApr2023_Kalauhaihai <- read_csv(here("raw_data/raw_pH/data_pH_FebApr2023_Kalauhaihai_20839036.csv"))
```

```{r FebApr2023 Kanewai, message=FALSE, warning=FALSE}
data_pH_FebApr2023_KanewaiSpringRock <- read_csv(here("raw_data/raw_pH/data_pH_FebApr2023_KanewaiSpringRock_21433529.csv"))
```

```{r Apr2023 Kalauhaihai, message=FALSE, warning=FALSE}
data_pH_Apr2022_Kalauhaihai <- read_tsv(here("raw_data/raw_pH/data_pH_Apr2022_Kalauhaihai_20839036.txt"), skip = 1)
```

# Clean Names

```{r}
data_pH_OctNov2022_Kalauhaihai <- data_pH_OctNov2022_Kalauhaihai %>% 
  clean_names()

data_pH_FebApr2023_Kalauhaihai <- data_pH_FebApr2023_Kalauhaihai %>% 
  clean_names()

data_pH_FebApr2023_KanewaiSpringRock <- data_pH_FebApr2023_KanewaiSpringRock %>% 
  clean_names()

data_pH_Apr2022_Kalauhaihai <- 
data_pH_Apr2022_Kalauhaihai %>% 
  clean_names()
```

# Merge date and time columns for data_pH_OctNov2022_Kalauhaihai

```{r message=FALSE, warning=FALSE}
data_pH_OctNov2022_Kalauhaihai <- data_pH_OctNov2022_Kalauhaihai %>%
  unite(date_time, date, time, sep = " ")

data_pH_OctNov2022_Kalauhaihai$date_time <- dmy_hms(data_pH_OctNov2022_Kalauhaihai$date_time)
```

# Rename Column Names
```{r column rename function pH}
mfhc_colname_pH <- function(a = NULL, b = NULL, c = NULL, d = NULL, e = NULL, w = "temp_celsius", x = "mv", y = "pH", z = "date_time" ){
  colnames(a)[which(names(a) == b)] <- w
  colnames(a)[which(names(a) == c)] <- x
  colnames(a)[which(names(a) == d)] <- y
  colnames(a)[which(names(a) == e)] <- z
  
  a <- a %>% 
    select(z, w, x, y)
  
  return(a)
}
```

```{r}
data_pH_OctNov2022_Kalauhaihai <- mfhc_colname_pH(a = data_pH_OctNov2022_Kalauhaihai, b = "temp_c_c_1", c = "m_v_mv_c_2", d = "p_h_c_4")
```

```{r}
data_pH_FebApr2023_Kalauhaihai <- mfhc_colname_pH(a = data_pH_FebApr2023_Kalauhaihai, b = "ch_1_temperature_c", c = "ch_2_millivolts_mv", d = "ch_3_p_h_p_h", e = "date_time_hst")
```

```{r}
data_pH_FebApr2023_KanewaiSpringRock <- mfhc_colname_pH(a = data_pH_FebApr2023_KanewaiSpringRock, b = "ch_1_temperature_c", c = "ch_2_millivolts_mv", d = "ch_3_p_h_p_h", e = "date_time_hst")
```

```{r}
data_pH_Apr2022_Kalauhaihai <- mfhc_colname_pH(a = data_pH_Apr2022_Kalauhaihai, b = "temp_c", c = "m_v", d = "p_h", e = "date_time_gmt_1000")
```

# Make data_pH_FebApr2023_KanewaiSpringRock and data_pH_FebApr2023_Kalauhaihai UTC class

```{r}
data_pH_FebApr2023_KanewaiSpringRock$date_time <- mdy_hms(data_pH_FebApr2023_KanewaiSpringRock$date_time)

data_pH_FebApr2023_Kalauhaihai$date_time <- mdy_hms(data_pH_FebApr2023_Kalauhaihai$date_time)

```

# Format data to be joined with other variables and locations

# Add location columns

```{r}
data_pH_OctNov2022_Kalauhaihai<- 
data_pH_OctNov2022_Kalauhaihai %>% 
  mutate(site = "Kalauhaihai")

data_pH_FebApr2023_Kalauhaihai <- data_pH_FebApr2023_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")

data_pH_FebApr2023_KanewaiSpringRock <- data_pH_FebApr2023_KanewaiSpringRock %>%
  mutate(site = "Kanewai")

data_pH_Apr2022_Kalauhaihai <- data_pH_Apr2022_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")
```

# Maybe Trimming
```{r}
data_pH_OctNov2022_Kalauhaihai <- 
  data_pH_OctNov2022_Kalauhaihai %>% 
  filter(date_time >= "2022-10-07 10:10:00" & date_time <= "2022-11-09 9:30:00")

data_pH_FebApr2023_Kalauhaihai <-
  data_pH_FebApr2023_Kalauhaihai %>% 
  filter(date_time >= "2023-02-16 9:52:00" & date_time <= "2023-04-05 09:35:00")

data_pH_FebApr2023_KanewaiSpringRock <-
  data_pH_FebApr2023_KanewaiSpringRock %>% 
  filter(date_time >= "2023-02-09 9:52:00" & date_time <= "2023-04-05 10:15:00")

data_pH_Apr2022_Kalauhaihai <-
  data_pH_Apr2022_Kalauhaihai %>% 
  filter(date_time >= "2022-04-09 15:10:00" & date_time <= "2022-04-19 09:30:00")

```

# Join pH Data

```{r}
pH_joined <- bind_rows(data_pH_Apr2022_Kalauhaihai, data_pH_OctNov2022_Kalauhaihai, data_pH_FebApr2023_Kalauhaihai, data_pH_FebApr2023_KanewaiSpringRock)
```

# Format joined data to be joined with other variables and locations
```{r}
pH_joined <- pH_joined %>% 
  pivot_longer(temp_celsius:pH, 
               names_to = "variable",
               values_to = "value")
```

```{r}
pH_joined <- pH_joined %>% 
filter(variable == "pH")
```

# Write csv into cleaned_conductivity folder

```{r}
write_csv(pH_joined, here("cleaned_data/cleaned_pH/pH_joined.csv"))
```










