---
title: "Conductivity Cleaning"
author: "Connor Flynn"
date: "7/13/2023"
output: html_document
---

Load in packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```


# Read in Conductivity Data - 3 datsets

```{r Read in Kalauhaihai FebApr2023 Data, warning=FALSE}
data_conductivity_FebApr2023_Kalauhaihai <- read_csv(here("raw_data/raw_conductivity/data_conductivity_FebApr2023_Kalauhaihai_21415543.csv"), skip = 1)
```

```{r, warning=FALSE}
data_conductivity_FebApr2023_Kanewai <- read_csv(here("raw_data/raw_conductivity/data_conductivity_FebApr2023_Kanewai_21415544.csv"), skip = 1) # doesn't have a low range measurement
```

```{r message=FALSE, warning=FALSE}
data_conductivity_OctNov2022_Kalauhaihai <- read_tsv(here("raw_data/raw_conductivity/data_conductivity_OctNov2022_Kalauhaihai_21415543.txt"))
```



# Clean Names


```{r}
data_conductivity_FebApr2023_Kalauhaihai <- data_conductivity_FebApr2023_Kalauhaihai %>% 
  clean_names()
```

```{r}
data_conductivity_FebApr2023_Kanewai <- data_conductivity_FebApr2023_Kanewai %>% 
  clean_names()
```

```{r}
data_conductivity_OctNov2022_Kalauhaihai <- data_conductivity_OctNov2022_Kalauhaihai %>% 
  clean_names()
```

# Merge date and time columns for data_conductivity_OctNov2022_Kalauhaihai

```{r}
data_conductivity_OctNov2022_Kalauhaihai <- data_conductivity_OctNov2022_Kalauhaihai %>%
  unite(date_time, date, time, sep = " ")

data_conductivity_OctNov2022_Kalauhaihai$date_time <- mdy_hms(data_conductivity_OctNov2022_Kalauhaihai$date_time)
```



# Rename Column Names 

```{r}
colnames(data_conductivity_FebApr2023_Kalauhaihai)[which(names(data_conductivity_FebApr2023_Kalauhaihai) == "low_range_m_s_cm_lgr_s_n_21415543_sen_s_n_21415543")] <- "low_range_microSiemens"

colnames(data_conductivity_FebApr2023_Kalauhaihai)[which(names(data_conductivity_FebApr2023_Kalauhaihai) == "high_range_m_s_cm_lgr_s_n_21415543_sen_s_n_21415543")] <- "high_range_microSiemens"

colnames(data_conductivity_FebApr2023_Kalauhaihai)[which(names(data_conductivity_FebApr2023_Kalauhaihai) == "temp_c_lgr_s_n_21415543_sen_s_n_21415543")] <- "temp_celsius"

colnames(data_conductivity_FebApr2023_Kalauhaihai)[which(names(data_conductivity_FebApr2023_Kalauhaihai) == "date_time_gmt_10_00")] <- "date_time"

data_conductivity_FebApr2023_Kalauhaihai <- data_conductivity_FebApr2023_Kalauhaihai %>% 
  select(date_time, low_range_microSiemens, high_range_microSiemens, temp_celsius)
```


```{r}
colnames(data_conductivity_FebApr2023_Kanewai)[which(names(data_conductivity_FebApr2023_Kanewai) == "high_range_m_s_cm_lgr_s_n_21415544_sen_s_n_21415544")] <- "high_range_microSiemens"

colnames(data_conductivity_FebApr2023_Kanewai)[which(names(data_conductivity_FebApr2023_Kanewai) == "temp_c_lgr_s_n_21415544_sen_s_n_21415544")] <- "temp_celsius"

colnames(data_conductivity_FebApr2023_Kanewai)[which(names(data_conductivity_FebApr2023_Kanewai) == "date_time_gmt_10_00")] <- "date_time"

data_conductivity_FebApr2023_Kanewai <- data_conductivity_FebApr2023_Kanewai %>% 
  select(date_time, high_range_microSiemens, temp_celsius)
```

```{r}
colnames(data_conductivity_OctNov2022_Kalauhaihai)[which(names(data_conductivity_OctNov2022_Kalauhaihai) == "low_range_m_s_cm_c_1_3")] <- "low_range_microSiemens"

colnames(data_conductivity_OctNov2022_Kalauhaihai)[which(names(data_conductivity_OctNov2022_Kalauhaihai) == "high_range_m_s_cm_c_1_3")] <- "high_range_microSiemens"

colnames(data_conductivity_OctNov2022_Kalauhaihai)[which(names(data_conductivity_OctNov2022_Kalauhaihai) == "temp_c_c_3")] <- "temp_celsius"


data_conductivity_OctNov2022_Kalauhaihai <- data_conductivity_OctNov2022_Kalauhaihai %>% 
  select(date_time, low_range_microSiemens, high_range_microSiemens, temp_celsius)
```

# Make data_conductivity_FebApr2023_Kanewai and data_conductivity_FebApr2023_Kalauhaihai UTC class

```{r}
data_conductivity_FebApr2023_Kanewai$date_time <- mdy_hms(data_conductivity_FebApr2023_Kanewai$date_time)
```


```{r}
data_conductivity_FebApr2023_Kalauhaihai$date_time <- mdy_hms(data_conductivity_FebApr2023_Kalauhaihai$date_time)
```

# Format data to be joined with other variables and locations

# Add location columns

```{r}
data_conductivity_FebApr2023_Kalauhaihai <- data_conductivity_FebApr2023_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")

data_conductivity_FebApr2023_Kanewai <- data_conductivity_FebApr2023_Kanewai %>%
  mutate(site = "Kanewai")

data_conductivity_OctNov2022_Kalauhaihai <- data_conductivity_OctNov2022_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")
```

# Maybe Trimming

# Join Conductivity Data

```{r}
conductivity_joined <- bind_rows(data_conductivity_FebApr2023_Kalauhaihai,
                                 data_conductivity_FebApr2023_Kanewai,
                                 data_conductivity_OctNov2022_Kalauhaihai)
```

# Format joined data to be joined with other variables and locations

```{r}
conductivity_joined <- conductivity_joined %>% 
  pivot_longer(low_range_microSiemens:temp_celsius, 
               names_to = "variable",
               values_to = "value")
```


Write csv into cleaned_conductivity folder

```{r}
write_csv(conductivity_joined, here("cleaned_data/cleaned_conductivity/conductivity_joined.csv"))
```

