---
title: "Oxygen Cleaning"
author: "Anson Ekau"
date: "7/14/2023"
output: html_document
---

Load in packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```


# Read in Dissolved Oxygen data — 4 sets

```{r OctNov2022 Kalauhaihai, message=FALSE, warning=FALSE}
data_oxygen_OctNov2022_Kalauhaihai <- read_tsv(here("raw_data/raw_oxygen/data_oxygen_OctNov2022_Kalauhaihai_21446085.txt"))
```

```{r FebApr2023 Kalauhaihai, message=FALSE, warning=FALSE}
data_oxygen_FebApr2023_Kalauhaihai <- read_csv(here("raw_data/raw_oxygen/Data_oxygen_FebApr2023_Kalauhaihai_21446085.csv"), skip = 1)
```

```{r FebApr2023 Kanewai, message=FALSE, warning=FALSE}
data_oxygen_FebApr2023_KanewaiSpringRock <- read_csv(here("raw_data/raw_oxygen/Data_oxygen_FebApr2023_KanewaiSpringRock_21515403.csv"), skip = 1)
```

```{r AprMay2023 Kalauhaihai, message=FALSE, warning=FALSE}
data_oxygen_AprMay2023_Kalauhaihai <- read_csv(here("raw_data/raw_oxygen/data_oxygen_AprMay2023_Kalauhaihai_21446085.csv"), skip = 1)
```

# Clean Names


```{r}
data_oxygen_OctNov2022_Kalauhaihai <- data_oxygen_OctNov2022_Kalauhaihai %>% 
  clean_names()
```

```{r}
data_oxygen_FebApr2023_Kalauhaihai <- data_oxygen_FebApr2023_Kalauhaihai %>% 
  clean_names()
```

```{r}
data_oxygen_FebApr2023_KanewaiSpringRock <- data_oxygen_FebApr2023_KanewaiSpringRock %>% 
  clean_names()
```

```{r}
data_oxygen_AprMay2023_Kalauhaihai <- 
data_oxygen_AprMay2023_Kalauhaihai %>% 
  clean_names()
```

# Merge date and time columns for data_oxygen_OctNov2022_Kalauhaihai

```{r message=FALSE, warning=FALSE}
data_oxygen_OctNov2022_Kalauhaihai <- data_oxygen_OctNov2022_Kalauhaihai %>%
  unite(date_time, date, time, sep = " ")

data_oxygen_OctNov2022_Kalauhaihai$date_time <- mdy_hms(data_oxygen_OctNov2022_Kalauhaihai$date_time)
```

# Rename Column Names
```{r}
colnames(data_oxygen_OctNov2022_Kalauhaihai)[which(names(data_oxygen_OctNov2022_Kalauhaihai) == "do_conc_mg_l_c_1_2")] <- "dissolved_oxygen_mg_l"

colnames(data_oxygen_OctNov2022_Kalauhaihai)[which(names(data_oxygen_OctNov2022_Kalauhaihai) == "temp_c_c_2")] <- "temp_celsius"

data_oxygen_OctNov2022_Kalauhaihai <-
data_oxygen_OctNov2022_Kalauhaihai %>% 
  select(date_time, dissolved_oxygen_mg_l, temp_celsius)
```

# Create a function to change column oxygen data sets
```{r oxygen rename function}
mfhc_rename_DO <- function(a = NULL, b = NULL, c = NULL, x = "dissolved_oxygen_mg_l", y = "temp_celsius", z = "date_time") {
  colnames(a)[which(names(a) == b)] <- x
  colnames(a)[which(names(a) == c)] <- y
  colnames(a)[which(names(a) == "date_time_gmt_10_00")] <- z
  
  a <- a %>% 
    select(z, x, y)
  
  return(a)
}
```

```{r}
data_oxygen_FebApr2023_Kalauhaihai <- mfhc_rename_DO(a = data_oxygen_FebApr2023_Kalauhaihai, b = "do_conc_mg_l_lgr_s_n_21446085_sen_s_n_21446085", c = "temp_c_lgr_s_n_21446085_sen_s_n_21446085")
```

```{r}
data_oxygen_FebApr2023_KanewaiSpringRock <- mfhc_rename_DO(a = data_oxygen_FebApr2023_KanewaiSpringRock, b = "do_conc_mg_l_lgr_s_n_21515403_sen_s_n_21515403", c = "temp_c_lgr_s_n_21515403_sen_s_n_21515403")
```

```{r}
data_oxygen_AprMay2023_Kalauhaihai <- mfhc_rename_DO(a = data_oxygen_AprMay2023_Kalauhaihai, b = "do_conc_mg_l_lgr_s_n_21446085_sen_s_n_21446085", c = "temp_c_lgr_s_n_21446085_sen_s_n_21446085")
```

# Make data_oxygen_FebApr2023_Kalauhaihai, data_oxygen_FebApr2023_KanewaiSpringRock,and data_oxygen_AprMay2023_Kalauhaihai UTC class

```{r}
data_oxygen_FebApr2023_Kalauhaihai$date_time <- mdy_hms(data_oxygen_FebApr2023_Kalauhaihai$date_time)

data_oxygen_FebApr2023_KanewaiSpringRock$date_time <- mdy_hms(data_oxygen_FebApr2023_KanewaiSpringRock$date_time)

data_oxygen_AprMay2023_Kalauhaihai$date_time <- mdy_hms(data_oxygen_AprMay2023_Kalauhaihai$date_time)
```

# Format data to be joined with other variables and locations

# Add location columns

```{r}
data_oxygen_OctNov2022_Kalauhaihai<- 
data_oxygen_OctNov2022_Kalauhaihai %>% 
  mutate(site = "Kalauhaihai")

data_oxygen_FebApr2023_Kalauhaihai <- data_oxygen_FebApr2023_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")

data_oxygen_FebApr2023_KanewaiSpringRock <- data_oxygen_FebApr2023_KanewaiSpringRock %>%
  mutate(site = "Kanewai")

data_oxygen_AprMay2023_Kalauhaihai <- data_oxygen_AprMay2023_Kalauhaihai %>%
  mutate(site = "Kalauhaihai")
```

# Maybe Trimming

# Join Oxygen Data

```{r}
oxygen_joined <- bind_rows(data_oxygen_OctNov2022_Kalauhaihai, data_oxygen_FebApr2023_Kalauhaihai, data_oxygen_FebApr2023_KanewaiSpringRock, data_oxygen_AprMay2023_Kalauhaihai)

```

# Format joined data to be joined with other variables and locations

```{r}
oxygen_joined <- oxygen_joined %>% 
  pivot_longer(dissolved_oxygen_mg_l:temp_celsius, 
               names_to = "variable",
               values_to = "value")
```


# Write csv into cleaned_conductivity folder

```{r}
write_csv(oxygen_joined, here("cleaned_data/cleaned_oxygen/oxygen_joined.csv"))
```

