---
title: "Can we For Loop!?"
author: "Connor Flynn"
date: "4/25/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #A toolbox full of more toolboxes
library(here) #Sets working directory, type the following in console or in a code chunk. 'here::set_here()' 
library(janitor) #Used to clean names
library(plotly) #Used to make ggplots interactive
```


#Set Up
The "Set Up" sections sets the working directory using the here() function. It also defines the path to the raw data folder and the specific variable folder. Inside the variable folders are the raw data files. 
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Set the working directory to the project root folder
here::set_here()

# Define the path to the raw data folder
raw_data_folder <- here("raw_data", "raw_pH")

# Get the list of files in the raw_pH folder
file_list <- list.files(path = raw_data_folder, full.names = TRUE)

# Define a function to read and clean the column names
read_and_clean_data <- function(file_path) {
  # Check if file is .csv or .txt
  file_ext <- tools::file_ext(file_path)
  
  # Read the file based on the extension
  if (file_ext == "csv") {
    data <- read_csv(file_path)
  } else if (file_ext == "txt") {
    data <- read_tsv(file_path)
  } else {
    stop("Unsupported file format")
  }

  if (file_ext == "csv") {
  data <- read_csv(file_path)
} else if (file_ext == "txt") {
  # Read the first line to check if it starts with "Serial"
  first_line <- readLines(file_path, n = 1)

  if (startsWith(first_line, "Serial")) {
    data <- read_tsv(file_path, skip = 1)
  } else {
    data <- read_tsv(file_path)
  }
} else {
  stop("Unsupported file format")
}



  # Clean column names using janitor's clean_names()
  data <- data %>% clean_names()

  return(data)
}


# Loop through each file, read, and clean the data
for (i in seq_along(file_list)) {
  data <- read_and_clean_data(file_list[i])
  
  # Extract site information from file name
  if (grepl("Kalauhaihai", file_list[i])) {
    data$site <- "Kalauhaihai"
  } else if (grepl("Kanewai", file_list[i])) {
    data$site <- "Kanewai"
  }
  
  # Change columns containing "date" in their names to "date_time_hst"
  date_columns <- grep("date", colnames(data), ignore.case = TRUE)
  if (length(date_columns) > 0) {
    colnames(data)[date_columns] <- "date_time_hst"
  }
  
  # Change columns containing "p_h" in their names to "pH"
  ph_columns <- grep("p_h", colnames(data), ignore.case = TRUE)
  if (length(ph_columns) > 0) {
    colnames(data)[ph_columns] <- "pH"
  }

  # Merge date and time columns into a single datetime column
  if ("date_time_hst" %in% colnames(data) && "time" %in% colnames(data)) {
    data <- data %>%
      mutate(date_time_hst = as.POSIXct(paste(date_time_hst, time), format = "%d-%m-%y %H:%M:%S"))
  }
  
  # Set the class of "date_time_hst" column to POSIXct with the specified format
  if ("date_time_hst" %in% colnames(data)) {
    date_format <- c("%m/%d/%Y %H:%M:%S", "%Y-%m-%d %H:%M:%S", "%Y-%m-%d %H:%M:%S %Z")
    for (format in date_format) {
      data$date_time_hst <- as.POSIXct(data$date_time_hst, format = format, tz = "UTC", tryFormats = c(format))
    }
  }
  
  # Assign each dataframe to a variable based on file index
  assign(paste0("df", i), data)
}


```

```{r}
# Trimming
df5 <- 
  df5 %>% 
  filter(date_time_hst >= "2022-10-07 10:10:00" & date_time_hst <= "2022-11-09 9:30:00")

df2 <-
  df2 %>% 
  filter(date_time_hst >= "2023-02-16 9:52:00" & date_time_hst <= "2023-04-05 09:35:00")

df3 <-
  df3 %>% 
  filter(date_time_hst >= "2023-02-09 9:52:00" & date_time_hst <= "2023-04-05 10:15:00")

df1 <-
  df1 %>% 
  filter(date_time_hst >= "2022-04-09 15:10:00" & date_time_hst <= "2022-04-19 09:30:00")

df4 <-
  df4 %>% 
  filter(date_time_hst >= "2023-07-12 16:40:00" & date_time_hst <= "2023-09-17 13:25:00")

```

```{r}
# join
pH_joined <- bind_rows(df1, df2, df3, df4, df5) %>% 
  select(date_time_hst, pH, site)


```

```{r}
a <- ggplot(pH_joined, aes(x = date_time_hst, 
                      y = pH, color = site)) +
  geom_line(size = 0.1) +
  theme_minimal()

ggplotly(a)
```
Notes:

- Maybe leave out df1 because it's only 2 weeks of data with major gap until next hobo deployed
- Trim
- Add locations
- Need Feb - April 2024 pH data (both sites)
  - in logger notes but not in pH folder


Trimming 

Kalauhaihai July - Sept 2023
- 7/12/2023 16:40:00
- 9/18/2023 13:25:00

Kalauhaihai Oct-Nov 2022
- 10/6/2022 10:10:00
- 11/10/2022 9:30:00

Kalauhaihai Feb-April 2023
- 2/16/2023 9:52:00
- 4/6/2023 9:35:00

Kanewai Feb-April 2023
- 2/9/2023 10:13:00
- 4/6/2023 10:15:00





