---
title: "temperature_clean_test"
author: "Anson Ekau"
date: "2024-05-30"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #A toolbox full of more toolboxes
library(here) #Sets working directory, type the following in console or in a code chunk. 'here::set_here()' 
library(janitor) #Used to clean names
library(plotly) #Used to make ggplots interactive
```

#Set up The "Set Up" sections sets the working directory using the
here() function. It also defines the path to the raw data folder and the
specific variable folder. Inside the variable folders are the raw data
files.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Set the working directory to the project root folder
here::set_here()

# Define the path to the raw data folder
raw_data_folder <- here("raw_data", "raw_temperature")

# Get the list of files in the raw_pH folder
file_list <- list.files(path = raw_data_folder, full.names = TRUE)

# List of site names to check for
site_names <- c("Garage", "Makaha", "Auwai", "Norfolk", "Highway", "Shade", "Octopus", "Rock", "Berry", "Springledge", "Coconut")


```

#Define Read and Clean Function The following chunk creates a function
using loops to read in the raw data files. The files come in .txt and
.csv. This is important to note because reading in these files uses
different functions and specific arguments need to be set to read them
in correctly.

```{r}
# Define a function to read and clean the column names
read_and_clean_data <- function(file_path) {
  # Check if file is .csv or .txt
  file_ext <- tools::file_ext(file_path)
  
  if (file_ext == "csv") {
  data <- read_csv(file_path, skip = 1)
} else if (file_ext == "txt") {
  # Read the first line to check if it starts with "Serial"
  first_line <- readLines(file_path, n = 1)

  if (startsWith(first_line, "Serial")) {
    data <- read_tsv(file_path, skip = 1)
  } else {
    data <- read_tsv(file_path)
  }
} else {
  stop("Unsupported file format")
}



  # Clean column names using janitor's clean_names()
  data <- data %>% clean_names()

  return(data)
}
```

#Reading in and cleaning The following section is reading in the data
and cleaning it. Again using loops the data is read in using the
function created in the previous section. After a 'site' column is added
that species which location the data comes from. It also renames certain
columns to clean and combine them more efficiently. The classes of the
columns are also changed to the correct class so they work later in
binding, trimming, and visualizing in the following sections.

When reading in a text file there will most likely be separate date and
time column. CSV files will have a combined date time column. Its
important to check if there are multiple formats for the date time
columns.

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(lubridate)

for (i in seq_along(file_list)) {
  data <- read_and_clean_data(file_list[i])

  # Add site location
  if (grepl("Kalauhaihai", file_list[i], ignore.case = TRUE)) {
    data$site <- "Kalauhaihai"
  } else if (grepl("Kanewai", file_list[i], ignore.case = TRUE)) {
    data$site <- "Kanewai"
  }

  # Site-specific tag
  for (site_name in site_names) {
    if (grepl(site_name, file_list[i], ignore.case = TRUE)) {
      data$site_specific <- site_name
      break
    }
  }

  # Standardize column names
  date_columns <- grep("date", names(data), ignore.case = TRUE)
  if (length(date_columns) > 0) {
    names(data)[date_columns] <- "date_time_hst"
  }

  temp_columns <- grep("temp", names(data), ignore.case = TRUE)
  if (length(temp_columns) > 0) {
    names(data)[temp_columns] <- "temperature"
  }

  # ---- Robust datetime parse (AM/PM or 24h) ----
  datetime_str <- NULL
  if ("date_time_hst" %in% names(data) && "time" %in% names(data)) {
    datetime_str <- paste(as.character(data$date_time_hst), as.character(data$time))
  } else if ("date_time_hst" %in% names(data)) {
    datetime_str <- as.character(data$date_time_hst)
  }

  if (!is.null(datetime_str)) {
    tz_hst <- "Pacific/Honolulu"

    am_pm_present <- any(grepl("\\b(AM|PM)\\b", datetime_str, ignore.case = TRUE), na.rm = TRUE)

    orders_am_pm <- c("mdy HMS p","dmy HMS p","ymd HMS p","mdy HM p","dmy HM p","ymd HM p")
    orders_24h   <- c("mdy HMS","dmy HMS","ymd HMS","mdy HM","dmy HM","ymd HM")
    orders <- if (am_pm_present) orders_am_pm else orders_24h

    dt <- parse_date_time(datetime_str, orders = orders, tz = tz_hst, quiet = TRUE)

    if (sum(is.na(dt)) > 0.5 * length(dt)) {
      backup_orders <- if (am_pm_present) orders_24h else orders_am_pm
      dt2 <- parse_date_time(datetime_str, orders = backup_orders, tz = tz_hst, quiet = TRUE)
      dt[is.na(dt)] <- dt2[is.na(dt)]
    }

    # Ensure POSIXct and normalize display to 24-hour:
    # 1) strftime to "%Y-%m-%d %H:%M:%S" (24h),
    # 2) parse back to POSIXct so the column stays datetime (not character).
    data$date_time_hst <- as.POSIXct(
      strftime(dt, format = "%Y-%m-%d %H:%M:%S", tz = tz_hst),
      tz = tz_hst
    )
  }

  # Save out
  assign(tolower(gsub("\\..*", "", basename(file_list[i]))), data, envir = .GlobalEnv)
}


```

#Trimming The following section is trimming the data and removing the
times the loggers were out of the water.

This is where manual input is needed. Manually add the new data name,
and the specific time the logger was in and out of the water. Refer to
the video for help in this section.

Format: 'replace this with the data name' \<- 'replace this with the
data name' %\>% filter(date_time_hst \>= "year-month-day
hour:minute:sec" & date_time_hst \<= "year-month-day hour:minute:sec)

Example: data_temp_sept2021feb2022_kalauhaihaiauwaiunderbridge_20970094
\<- data_temp_sept2021feb2022_kalauhaihaiauwaiunderbridge_20970094 %\>%
filter(date_time_hst \>= "2021-09-13 13:00:00" & date_time_hst \<=
"2022-02-16 9:00:00")

```{r}
# Trimming
data_temp_sept2021feb2022_kalauhaihaiauwaiunderbridge_20970094 <- data_temp_sept2021feb2022_kalauhaihaiauwaiunderbridge_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2021-09-13 13:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-02-16 9:00:00", tz = "Pacific/Honolulu"))

data_temp_sept2021june2022_kalauhaihaimakaha_20970115 <- data_temp_sept2021june2022_kalauhaihaimakaha_20970115 %>% 
  filter(date_time_hst >= ymd_hms("2021-09-13 13:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-06-09 15:55:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaiauwai_20970122 <- data_temp_marapr2022_kalauhaihaiauwai_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaicoconuttree_20970110 <- data_temp_marapr2022_kalauhaihaicoconuttree_20970110 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaigarage_20970094 <- data_temp_marapr2022_kalauhaihaigarage_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaihighway_20970092 <- data_temp_marapr2022_kalauhaihaihighway_20970092 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaimakaha_20970102 <- data_temp_marapr2022_kalauhaihaimakaha_20970102 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_marapr2022_kalauhaihaioctopustree_20970118 <- data_temp_marapr2022_kalauhaihaioctopustree_20970118 %>% 
  filter(date_time_hst >= ymd_hms("2022-03-03 10:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-04-20 9:30:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kalauhaihaigarage_20970092 <- data_temp_juneoct2022_kalauhaihaigarage_20970092 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 15:55:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-05 9:30:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kalauhaihaimakaha_20970109 <- data_temp_juneoct2022_kalauhaihaimakaha_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 15:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-05 9:40:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kanewaiauwaimakaisidefootbridge_20970107 <- data_temp_juneoct2022_kanewaiauwaimakaisidefootbridge_20970107 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 15:05:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-09 14:50:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kanewaifishpondshadeunderxmasberry_20970123 <- data_temp_juneoct2022_kanewaifishpondshadeunderxmasberry_20970123 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 2:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-09 15:00:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kanewaifishpondledgeedgenorfolk_20970122 <- data_temp_juneoct2022_kanewaifishpondledgeedgenorfolk_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 15:20:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-09 14:45:00", tz = "Pacific/Honolulu"))

data_temp_juneoct2022_kanewaispringledge_20970093 <- data_temp_juneoct2022_kanewaispringledge_20970093 %>% 
  filter(date_time_hst >= ymd_hms("2022-06-10 14:45:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-10-09 15:05:00", tz = "Pacific/Honolulu"))

data_temp_octnov2022_kalauhaihaigarage_21445019 <- data_temp_octnov2022_kalauhaihaigarage_21445019 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-06 10:10:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-11-09 9:30:00", tz = "Pacific/Honolulu"))

data_temp_octnov2022_kalauhaihaimakaha_21445021 <- data_temp_octnov2022_kalauhaihaimakaha_21445021 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-06 10:10:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2022-11-09 9:30:00", tz = "Pacific/Honolulu"))

data_temp_oct2022feb2023_kanewaiauwaimakaisidefootbridge_20970110 <- data_temp_oct2022feb2023_kanewaiauwaimakaisidefootbridge_20970110 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-10 15:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-08 10:29:00", tz = "Pacific/Honolulu"))

data_temp_oct2022feb2023_kanewaifishpondledgeedgenorfolk_20970094 <- data_temp_oct2022feb2023_kanewaifishpondledgeedgenorfolk_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-10 14:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-08 10:51:00", tz = "Pacific/Honolulu"))

data_temp_oct2022feb2023_kanewaifishpondshadeunderxmasberry_20970115 <- data_temp_oct2022feb2023_kanewaifishpondshadeunderxmasberry_20970115 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-10 15:05:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-08 10:31:00", tz = "Pacific/Honolulu"))

data_temp_oct2022feb2023_kanewaispringledge_20970102 <- data_temp_oct2022feb2023_kanewaispringledge_20970102 %>% 
  filter(date_time_hst >= ymd_hms("2022-10-10 15:10:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-08 10:43:00", tz = "Pacific/Honolulu"))

data_temp_nov2022feb2023_kalauhaihaigarage_20970109 <- data_temp_nov2022feb2023_kalauhaihaigarage_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2022-11-10 9:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-15 09:27:00", tz = "Pacific/Honolulu"))

data_temp_nov2022feb2023_kalauhaihaimakaha_20970123 <- data_temp_nov2022feb2023_kalauhaihaimakaha_20970123 %>% 
  filter(date_time_hst >= ymd_hms("2022-11-10 9:50:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-02-15 09:31:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kalauhaihaigarage_20970122 <- data_temp_febapr2023_kalauhaihaigarage_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-16 9:52:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 09:35:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kalauhaihaimakaha_20970107 <- data_temp_febapr2023_kalauhaihaimakaha_20970107 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-16 9:32:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 09:48:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kanewaiauwaimakaisidefootbridge_20970093 <- data_temp_febapr2023_kanewaiauwaimakaisidefootbridge_20970093 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-09 10:31:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 10:17:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kanewaifishpondledgeedgenorfolk_20970108 <- data_temp_febapr2023_kanewaifishpondledgeedgenorfolk_20970108 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-09 10:53:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 10:25:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kanewaifishpondshadeunderxmasberry_21445019 <- data_temp_febapr2023_kanewaifishpondshadeunderxmasberry_21445019 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-09 10:32:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 10:21:00", tz = "Pacific/Honolulu"))

data_temp_febapr2023_kanewaispringledge_20970092 <- data_temp_febapr2023_kanewaispringledge_20970092 %>% 
  filter(date_time_hst >= ymd_hms("2022-02-09 10:47:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-04-05 10:32:00", tz = "Pacific/Honolulu"))

data_temp_aproct2023_kalauhaihaigarage_20970102 <- data_temp_aproct2023_kalauhaihaigarage_20970102 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 9:46:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-10-05 9:24:00", tz = "Pacific/Honolulu"))

data_temp_aproct2023_kalauhaihaimakaha_21445021 <- data_temp_aproct2023_kalauhaihaimakaha_21445021 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 9:49:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-10-05 9:33:00", tz = "Pacific/Honolulu"))

data_temp_octnov2023_kalauhaihaigarage_20970108 <- data_temp_octnov2023_kalauhaihaigarage_20970108 %>% 
  filter(date_time_hst >= ymd_hms("2023-10-05 1:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-07 2:56:33", tz = "Pacific/Honolulu"))

data_temp_octnov2023_kalauhaihaimakaha_20970107 <- data_temp_octnov2023_kalauhaihaimakaha_20970107 %>% 
  filter(date_time_hst >= ymd_hms("2023-10-05 1:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-07 2:49:10", tz = "Pacific/Honolulu"))

data_temp_aproct2023_kanewaifishpondledgeedgenorfolk_20970110 <- data_temp_aproct2023_kanewaifishpondledgeedgenorfolk_20970110 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 10:27:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-10-05 10:17:00", tz = "Pacific/Honolulu"))

data_temp_aproct2023_kanewaifishpondshadeunderxmasberry_21445020 <- data_temp_aproct2023_kanewaifishpondshadeunderxmasberry_21445020 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 10:22:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-10-05 10:01:00", tz = "Pacific/Honolulu"))

data_temp_aproct2023_kanewaispringledge_20970109 <- data_temp_aproct2023_kanewaispringledge_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 10:34:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-10-05 10:08:00", tz = "Pacific/Honolulu"))

data_temp_aprnov2023_kanewaiauwai_21445022 <- data_temp_aprnov2023_kanewaiauwai_21445022 %>% 
  filter(date_time_hst >= ymd_hms("2023-04-06 10:19:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-02 10:11:00", tz = "Pacific/Honolulu"))

data_temp_novfeb2024_kalauhaihaigarage_20970109 <- data_temp_novfeb2024_kalauhaihaigarage_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2023-11-02 9:30:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-02-01 9:33:00", tz = "Pacific/Honolulu"))

data_temp_novfeb2024_kanewaiauwaiunderfootbridge_21445021 <- data_temp_novfeb2024_kanewaiauwaiunderfootbridge_21445021 %>% 
  filter(date_time_hst >= ymd_hms("2023-11-02 10:10:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-02-01 10:20:00", tz = "Pacific/Honolulu"))

data_temp_novfeb2024_kanewaifishpondedgenorfolk_20970123 <- data_temp_novfeb2024_kanewaifishpondedgenorfolk_20970123 %>% 
  filter(date_time_hst >= ymd_hms("2023-11-02 10:40:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-02-01 10:36:00", tz = "Pacific/Honolulu"))

data_temp_novfeb2024_kanewairockstairsbywall_20970115 <- data_temp_novfeb2024_kanewairockstairsbywall_20970115 %>% 
  filter(date_time_hst >= ymd_hms("2023-11-02 10:07:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-02-01 10:27:00", tz = "Pacific/Honolulu"))

data_temp_novfeb2024_kanewaispringledgemakaiend_20970094 <- data_temp_novfeb2024_kanewaispringledgemakaiend_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2023-11-02 10:33:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-02-01 10:31:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kalauhaihaigarage_21445019 <- data_temp_febapr2024_kalauhaihaigarage_21445019 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 9:40:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 9:42:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kalauhaihaimakaha_20970122 <- data_temp_febapr2024_kalauhaihaimakaha_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 9:47:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 9:59:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kanewaiauwaiunderfootbridge_20970102 <- data_temp_febapr2024_kanewaiauwaiunderfootbridge_20970102 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 10:22:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 10:35:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kanewaifishpondedgenorfolk_20970107 <- data_temp_febapr2024_kanewaifishpondedgenorfolk_20970107 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 10:37:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 10:43:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kanewairockstairsbywall_20970108 <- data_temp_febapr2024_kanewairockstairsbywall_20970108 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 10:29:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 10:32:00", tz = "Pacific/Honolulu"))

data_temp_febapr2024_kanewaispringledgemakaiend_21445022 <- data_temp_febapr2024_kanewaispringledgemakaiend_21445022 %>% 
  filter(date_time_hst >= ymd_hms("2024-02-01 10:33:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-04-04 10:39:00", tz = "Pacific/Honolulu"))

data_temp_aprsept2024_kanewaispringledgemakaiend_20970093 <- data_temp_aprsept2024_kanewaispringledgemakaiend_20970093 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-04 10:40:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 17:00:00", tz = "Pacific/Honolulu"))

data_temp_sept2024feb2025_kalauhaihaimakaha_21445022 <- data_temp_sept2024feb2025_kalauhaihaimakaha_21445022 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 16:15:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 09:39:00", tz = "Pacific/Honolulu"))


data_temp_aprsept2024_kalauhaihaimakaha_20970115 <- data_temp_aprsept2024_kalauhaihaimakaha_20970115 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-04 10:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 16:10:00", tz = "Pacific/Honolulu"))


data_temp_febapr2025_kalauhaihaimakaha_20970109 <- data_temp_febapr2025_kalauhaihaimakaha_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 9:39:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 9:56:00", tz = "Pacific/Honolulu"))

data_temp_febapr2025_kalauhaihaigarage_20970094 <- data_temp_febapr2025_kalauhaihaigarage_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 9:36:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 9:45:00", tz = "Pacific/Honolulu"))


data_temp_aprsept2024_kalauhaihaigarage_20970109 <- data_temp_aprsept2024_kalauhaihaigarage_20970109 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-02 9:44:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 15:45:00", tz = "Pacific/Honolulu"))

data_temp_sept2024feb2025_kalauhaihaigarage_20970122 <- data_temp_sept2024feb2025_kalauhaihaigarage_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 16:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 9:20:00", tz = "Pacific/Honolulu"))

data_temp_sept2024feb2025_kanewaispringledgemaukaend_20970092 <- data_temp_sept2024feb2025_kanewaispringledgemaukaend_20970092 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 17:10:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 10:35:00", tz = "Pacific/Honolulu"))

data_temp_sept2024feb2025_kanewaifishpondedgenorfolk_20970108 <- data_temp_sept2024feb2025_kanewaifishpondedgenorfolk_20970108 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 17:20:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 10:42:00", tz = "Pacific/Honolulu"))


data_temp_sept2024feb2025_kanewaiauwaiunderfootbridge_21445021 <- data_temp_sept2024feb2025_kanewaiauwaiunderfootbridge_21445021 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 17:00:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 10:26:00", tz = "Pacific/Honolulu"))

data_temp_sept2024feb2025_kanewairockstairsbywall_20970102 <- data_temp_sept2024feb2025_kanewairockstairsbywall_20970102 %>% 
  filter(date_time_hst >= ymd_hms("2024-09-20 16:55:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-02-06 10:20:00", tz = "Pacific/Honolulu"))

data_temp_aprsept2024_kanewaiauwaiunderfootbridge_20970094 <- data_temp_aprsept2024_kanewaiauwaiunderfootbridge_20970094 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-04 10:38:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 16:55:00", tz = "Pacific/Honolulu"))

data_temp_aprsept2024_kanewaifishpondedgenorfolk_21445020 <- data_temp_aprsept2024_kanewaifishpondedgenorfolk_21445020 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-04 10:44:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 17:15:00", tz = "Pacific/Honolulu"))

data_temp_aprsept2024_kanewairockstairsbywall_20970123 <- data_temp_aprsept2024_kanewairockstairsbywall_20970123 %>% 
  filter(date_time_hst >= ymd_hms("2024-04-04 10:33:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2024-09-20 16:50:00", tz = "Pacific/Honolulu"))

data_temp_octnov2023_kanewaifishpondedgenorfolk_20970122 <- data_temp_octnov2023_kanewaifishpondedgenorfolk_20970122 %>% 
  filter(date_time_hst >= ymd_hms("2023-10-05 10:18:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-02 10:37:00", tz = "Pacific/Honolulu"))


data_temp_octnov2023_kanewairockstairsbywall_20970092 <- data_temp_octnov2023_kanewairockstairsbywall_20970092 %>% 
  filter(date_time_hst >= ymd_hms("2023-10-05 10:25:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-02 10:05:00", tz = "Pacific/Honolulu"))


data_temp_octnov2023_kanewaispringledge_21445019 <- data_temp_octnov2023_kanewaispringledge_21445019 %>% 
  filter(date_time_hst >= ymd_hms("2023-10-05 10:12:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2023-11-02 10:22:00", tz = "Pacific/Honolulu"))


data_temp_febapr2025_kanewaiauwaiunderfootbridge_20970093 <- data_temp_febapr2025_kanewaiauwaiunderfootbridge_20970093 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 10:30:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 10:35:00", tz = "Pacific/Honolulu"))


data_temp_febapr2025_kanewaifishpondedgenorfolk_2097010 <- data_temp_febapr2025_kanewaifishpondedgenorfolk_20970107 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 10:44:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 10:43:00", tz = "Pacific/Honolulu"))


data_temp_febapr2025_kanewairockstairsbywall_21445020 <- data_temp_febapr2025_kanewairockstairsbywall_21445020 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 10:26:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 10:32:00", tz = "Pacific/Honolulu"))


data_temp_febapr2025_kanewaispringledgemaukaend_20970123 <- data_temp_febapr2025_kanewaispringledgemaukaend_20970123 %>% 
  filter(date_time_hst >= ymd_hms("2025-02-06 10:38:00", tz = "Pacific/Honolulu") & date_time_hst <= ymd_hms("2025-04-03 10:46:00", tz = "Pacific/Honolulu"))
```

#Join Data This last section joins the data. One again manual input is
needed. Add the new files separating by columns and new lines.

```{r}
# join
temperature_joined <- bind_rows(
data_temp_sept2021feb2022_kalauhaihaiauwaiunderbridge_20970094,
data_temp_sept2021june2022_kalauhaihaimakaha_20970115,
data_temp_marapr2022_kalauhaihaiauwai_20970122,
data_temp_marapr2022_kalauhaihaicoconuttree_20970110,
data_temp_marapr2022_kalauhaihaigarage_20970094,
#data_temp_marapr2022_kalauhaihaihighway_20970092,
data_temp_marapr2022_kalauhaihaimakaha_20970102,
#data_temp_marapr2022_kalauhaihaioctopustree_20970118,
data_temp_juneoct2022_kalauhaihaigarage_20970092,
data_temp_juneoct2022_kalauhaihaimakaha_20970109,
data_temp_juneoct2022_kanewaiauwaimakaisidefootbridge_20970107,
data_temp_juneoct2022_kanewaifishpondshadeunderxmasberry_20970123,
data_temp_juneoct2022_kanewaifishpondledgeedgenorfolk_20970122,
data_temp_juneoct2022_kanewaispringledge_20970093,
data_temp_octnov2022_kalauhaihaigarage_21445019,
data_temp_octnov2022_kalauhaihaimakaha_21445021,
data_temp_oct2022feb2023_kanewaiauwaimakaisidefootbridge_20970110,
data_temp_oct2022feb2023_kanewaifishpondledgeedgenorfolk_20970094,
data_temp_oct2022feb2023_kanewaifishpondshadeunderxmasberry_20970115,
data_temp_oct2022feb2023_kanewaispringledge_20970102,
data_temp_nov2022feb2023_kalauhaihaigarage_20970109,
data_temp_nov2022feb2023_kalauhaihaimakaha_20970123,
data_temp_febapr2023_kalauhaihaigarage_20970122,
data_temp_febapr2023_kalauhaihaimakaha_20970107,
data_temp_octnov2023_kalauhaihaigarage_20970108,
data_temp_octnov2023_kalauhaihaimakaha_20970107,
data_temp_febapr2023_kanewaiauwaimakaisidefootbridge_20970093,
data_temp_febapr2023_kanewaifishpondledgeedgenorfolk_20970108,
data_temp_febapr2023_kanewaifishpondshadeunderxmasberry_21445019,
data_temp_febapr2023_kanewaispringledge_20970092,
data_temp_aproct2023_kalauhaihaigarage_20970102,
data_temp_aproct2023_kalauhaihaimakaha_21445021,
data_temp_aproct2023_kanewaifishpondledgeedgenorfolk_20970110,
data_temp_aproct2023_kanewaifishpondshadeunderxmasberry_21445020,
data_temp_aproct2023_kanewaispringledge_20970109,
data_temp_aprnov2023_kanewaiauwai_21445022,
data_temp_novfeb2024_kalauhaihaigarage_20970109,
data_temp_novfeb2024_kanewaiauwaiunderfootbridge_21445021,
data_temp_novfeb2024_kanewaifishpondedgenorfolk_20970123,
data_temp_novfeb2024_kanewairockstairsbywall_20970115,
data_temp_novfeb2024_kanewaispringledgemakaiend_20970094,
data_temp_febapr2024_kalauhaihaigarage_21445019,
data_temp_febapr2024_kalauhaihaimakaha_20970122,
data_temp_febapr2024_kanewaiauwaiunderfootbridge_20970102,
data_temp_febapr2024_kanewaifishpondedgenorfolk_20970107,
data_temp_febapr2024_kanewairockstairsbywall_20970108,
data_temp_febapr2024_kanewaispringledgemakaiend_21445022,
data_temp_sept2024feb2025_kalauhaihaimakaha_21445022,
data_temp_aprsept2024_kalauhaihaimakaha_20970115,
data_temp_febapr2025_kalauhaihaimakaha_20970109,
data_temp_aprsept2024_kalauhaihaigarage_20970109,
data_temp_sept2024feb2025_kalauhaihaigarage_20970122,
data_temp_febapr2025_kalauhaihaigarage_20970094,
data_temp_sept2024feb2025_kanewaispringledgemaukaend_20970092,
data_temp_sept2024feb2025_kanewaifishpondedgenorfolk_20970108,
data_temp_sept2024feb2025_kanewaiauwaiunderfootbridge_21445021,
data_temp_sept2024feb2025_kanewairockstairsbywall_20970102,
data_temp_aprsept2024_kanewaiauwaiunderfootbridge_20970094,
data_temp_aprsept2024_kanewaifishpondedgenorfolk_21445020,
data_temp_aprsept2024_kanewairockstairsbywall_20970123,
data_temp_aprsept2024_kanewaispringledgemakaiend_20970093,
data_temp_octnov2023_kanewaifishpondedgenorfolk_20970122,
data_temp_octnov2023_kanewairockstairsbywall_20970092,
data_temp_octnov2023_kanewaispringledge_21445019,
data_temp_febapr2025_kanewaifishpondedgenorfolk_20970107,
data_temp_febapr2025_kanewaispringledgemaukaend_20970123,
data_temp_febapr2025_kanewairockstairsbywall_21445020,
data_temp_febapr2025_kanewaiauwaiunderfootbridge_20970093

) %>% 
  select(date_time_hst, temperature, site, site_specific)

```

#Write CSV

```{r}
write_csv(temperature_joined, here("cleaned_data/temp_joined.csv"))
```

```{r eval=FALSE, include=FALSE}
a <- ggplot(temperature_joined, aes(x = date_time_hst, 
                      y = temperature, color = site_specific)) +
  geom_line(size = 0.1) +
  theme_minimal()

ggplotly(a)
```
